% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%-------------------------------------------------------------------------------
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit (http://www.sascha-frank.com/latex-minipage.html - possible
% solution?)
% 2. Hacky space on the first bullet point on the second column.
%-------------------------------------------------------------------------------

\documentclass[]{deedy-resume-openfont}%
\begin{document}%
%
%-------------------------------------------------------------------------------
% Title Name
%-------------------------------------------------------------------------------
\namesection{Hatim}{Kanchwala}{Pre-final Year \textbullet{} Undergraduate \textbullet{} Electrical Engineering \textbullet{} Indian Institute of Technology Patna}{{\faMapMarker} A437, Boys' Hostel, IIT Patna, Amhara Village, Bihta, Bihar, India - 801118}{{\faMobile} (+91) 966 5154 719 \textbullet{} {\faEnvelopeO} \href{mailto:hatim@hatimak.me}{hatim@hatimak.me}, \href{mailto:hatim.ee14@iitp.ac.in}{hatim.ee14@iitp.ac.in} \textbullet{} {\faHome} \href{http://hatimak.me}{hatimak.me} \textbullet{} {\faGithub} \href{https://github.com/hatimak}{hatimak}}%
%
%-------------------------------------------------------------------------------
% Column One
%-------------------------------------------------------------------------------
\begin{minipage}[t]{0.25\textwidth} 
\begin{flushleft}%
%
%-------------------------------------------------------------------------------
% Interests
%-------------------------------------------------------------------------------
\section{Interests}
Computer Organisation \& Architecture \textbullet{} Embedded Systems Design \textbullet{} Adaptive Filters \textbullet{} Neural Networks \textbullet{} Entrepreneurship
\sectionsep
%
%-------------------------------------------------------------------------------
% Skills
%-------------------------------------------------------------------------------
\section{Skills}%
\subsection{Programming}%
C/C++ \textbullet{} Assembly \textbullet{} Verilog \textbullet{} JavaScript \textbullet{} Python \textbullet{} HTML/CSS \textbullet{} \LaTeX\ \textbullet{} Shell \textbullet{} \\
Java \textbullet{} OCaml
%
\subsection{Software}%
GNU/Linux \textbullet{} git/GitHub \textbullet{} MATLAB \textbullet{} Simulink \textbullet{} Xilinx \\
ISE \textbullet{} Multisim \textbullet{} Synopsys \textbullet{} Pyxis \textbullet{} MPLAB IDE \textbullet{} Proteus \textbullet{} NumPy/SciPy \textbullet{} Eclipse IDE
%
\subsection{Hardware}%
Xilinx Spartan FPGA \textbullet{} PIC Microcontroller \textbullet{} TMS320 DSP Chip \textbullet{} Arduino \textbullet{} 8051 Microcontroller \textbullet{} Raspberry \\
Pi \textbullet{} Teensy
%
\subsection{Languages}%
English \textbullet{} Hindi \textbullet{} Gujarati \textbullet{} Marathi \textbullet{} Urdu \textbullet{} Arabic
\sectionsep
%
%-------------------------------------------------------------------------------
% Education
%-------------------------------------------------------------------------------
\section{Education}%
\runsubsection{Indian Institute of Technology Patna \\}%
\descript{B. Tech. in Electrical Engineering}%
\location{{\faCalendar} 2014 - 2018 (expected)}%
\location{{\faMapMarker} Bihta (Bihar), India}%
CPI: 7.59 / 10.0 \small{(upto 5\textsuperscript{th} semester)}
\sectionsep
%
%-------------------------------------------------------------------------------
% Coursework
%-------------------------------------------------------------------------------
\section{Coursework}%
Digital Signal Processing \textbullet{} Analog Integrated Circuits \textbullet{} VLSI Design \textbullet{} Embedded Systems \textbullet{} Control Systems \textbullet{} Linear Algebra \textbullet{} Probability \& Random Processes \textbullet{} Machine Learning \textbullet{} Finance - Valuation \& Investing
\sectionsep
%
\end{flushleft}%
\end{minipage}%
\hfill
%
%-------------------------------------------------------------------------------
% Column Two
%-------------------------------------------------------------------------------
\begin{minipage}[t]{0.72\textwidth}%
%
%-------------------------------------------------------------------------------
% Projects
%-------------------------------------------------------------------------------
\section{Projects}%
\runsubsection{FPGA implementation of NLMS adaptive filtering algorithm for signal enhancement \\}%
\location{{\faCalendar} FEB. 2017 - PRESENT \textbullet{} {\faGithub} \href{https://github.com/hatimak/akagami}{hatimak/akagami}}%
\location{Adviser - Dr Yatendra Kumar Singh}%
\vspace{\topsep}% Hacky fix for awkward extra vertical space
\begin{tightemize}%
\item Implementing Normalized Least Mean Squares (NLMS) adaptive filtering algorithm to extract desired audio from corrupted signal with additive autoregressive noise.
\item Prototyping on Xilinx Spartan-3E FPGA in Verilog HDL, with focus towards optimised placing and routing.
\item Investigating performance gain by FPGA over typical DSP chip (TMS320).
\end{tightemize}%
\sectionsep
%
\runsubsection{8085 Instruction Set Architecture prototype on FPGA with basic pipelining \\}%
\location{{\faCalendar} JAN. 2017 - PRESENT \textbullet{} {\faGithub} \href{https://github.com/hatimak/marineford}{hatimak/marineford}}%
\location{Adviser - Dr Kailash Chandra Ray}%
\begin{tightemize}%
\item Implementing Intel 8085 microprocessor ISA on Xilinx Spartan-3E FPGA in Verilog HDL. Developing ASM testbenches to investigate performance gain due to pipelining.
\end{tightemize}%
\sectionsep
%
\runsubsection{Fingerprint based remote attendance system \\}%
\location{{\faCalendarCheckO} JAN. - OCT. 2015 \textbullet{} {\faGithub} \href{https://github.com/hatimak/den-den-mushi}{hatimak/den-den-mushi}}%
\begin{tightemize}%
\item
\end{tightemize}%
\sectionsep
%
%-------------------------------------------------------------------------------
% Experience
%-------------------------------------------------------------------------------
\section{Experience}%
\runsubsection{Aficionado Ventures}%
\descript{\textbullet{} Backend Engineer}%
\location{{\faBuildingO} Startup \textbullet{} {\faCalendarCheckO} FEB. 2016 - OCT. 2016 \textbullet{} {\faMapMarker} Gurugram (Haryana), India}%
\begin{tightemize}%
\item 
\end{tightemize}%
\sectionsep
%
\runsubsection{The Weave}%
\descript{\textbullet{} Co-founder \& Product Developer}%
\location{{\faBuildingO} Startup \textbullet{} {\faCalendarCheckO} JUNE 2015 - DEC. 2015 \textbullet{} {\faMapMarker} Patna (Bihar), India}%
\begin{tightemize}%
\item 
\end{tightemize}%
\sectionsep
%
%-------------------------------------------------------------------------------
% Extracurricular
%-------------------------------------------------------------------------------
\section{Extracurricular}%
\runsubsection{Coordinator, Startup Relations}%
\descript{\textbullet{} Entrepreneurship Club, IIT Patna}%
\location{{\faCalendar} APR 2015 - PRESENT}%
\begin{tightemize}
\item Serving as on-campus mentor to early stage startups, helping entrepreneurs develop business plan, choose investor strategy, and network with domain experts.
\item Responsible for building connections with startups and investors, and building investor panel for on-campus startups.
\item Part of Core Committee for E-Club’s flagship annual event, E-Week. Responsible for organizing guest talks, workshops and pitching event in collaboration with Incubation Centre, IIT Patna.
\end{tightemize}
\sectionsep
%
\end{minipage}%
\end{document}%
\documentclass[]{article}