\cvsection{Internships}

\begin{cventries}

\cventry
	{Student Developer, ``EDSAC Museum on FPGA''} % Job title
	{Free and Open Source Silicon Foundation} % Organization
	{Google Summer of Code 2017} % Location
	{May 2017 -- Aug. 2017} % Date(s)
	{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Replicated EDSAC architecture and ISA on myStorm Lattice iCE FPGA board using Verilog HDL and open-source toolchain Yosys.}
		\item {Designed and implemented modified-UART communication protocol for external extensible I/O interfaces.}
		\item {Final work product used at ChipHack workshop and presented work at ORConf 2017 conference during Wuthering Bytes festival in Hebden Bidge, UK.}
	\end{cvitems}}
%---------------------------------------------------------

\cventry
	{Student Developer, ``Read/Write Multiple Status Registers and Lock/Unlock Memory on SPI Chips''} % Job title
	{Flashrom} % Organization
	{Google Summer of Code 2016} % Location
	{Feb. 2016 -- Aug. 2016} % Date(s)
	{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Designed multiple status registers model to abstract chip diversities across manufacturers into single consistent interface.}
		\item {Developed routines to lock/unlock memory space governed by bits in status registers, handle configuration bits, and automatically generate memory protection maps for some chips.}
		\item {Added functionality to access/lock OTP memory areas.}
		\item {Developed CLI to expose new infrastructure. Tested on physical GigaDevice SPI chips using Raspberry Pi and Teensy.}
	\end{cvitems}}
%---------------------------------------------------------

\cventry
	{Summer Intern} % Job title
	{Aficionado Ventures} % Organization
	{Gurgaon, India} % Location
	{May. 2016 -- July 2016} % Date(s)
	{\begin{cvitems} % Description(s) of tasks/responsibilities
		\item {Aficionado was a startup helping restaurants procure quality produce from competitive collection of vendors.}
		\item {Designed reactive backend architecture - MeteorJS server, MongoDB database, Heroku/mLab web hosting, and Cordova for cross-platform mobile apps.}
		\item {Implemented MVP-stage marketplace platform with bilingual search for products in English/Hinglish.}
		\item {Worked with business team to conduct market research on restaurants and vendors.}
	\end{cvitems}}
%---------------------------------------------------------

\end{cventries}
