\begin{cvpositions}

\cvPositionOrganisation{}{\href{https://www.thedawoodibohras.com/about-the-bohras/faiz-al-mawaid-al-burhaniyah/}{Faiz al-Mawaid al-Burhaniyah} (FMB)} % Organisation

\cvPositionPost{EN}{Volunteer} % Post
\cvPositionPost{DE}{Freiwilliger} % Post

\cvPositionLocation{EN}{Aachen, Germany \ifbool{showEmojis} {\space\emoji{flag-germany}} {} } % Location
\cvPositionLocation{DE}{Aachen, Deutschland \ifbool{showEmojis} {\space\emoji{flag-germany}} {} } % Location

\cvPositionDates{EN}{June 2021 -- Apr. 2022} % Date(s)
\cvPositionDates{DE}{Juni 2021 -- Apr. 2022} % Date(s)

\cvPositionDescription{EN}{%
	\begin{cvitems} % Description(s)
		\item {Co-founded Aachen chapter of FMB and led team of volunteers to provide home-cooked and healthy meals to students in and around Aachen at least once a week.}
		\item {Organised meal distribution drives on festive occasions, especially Ramadan.}
%		\item {Liaised with FMB Frankfurt and FMB Strasbourg permanent members to manage operations and finance.} % TODO @hatimak: German version not written yet
%		\item {Co-developed low-cost, sustainable standard operating model to make community effort scalable and reproducible at other locations.} % TODO @hatimak: German version not written yet
	\end{cvitems}%
}
\cvPositionDescription{DE}{%
	\begin{cvitems} % Description(s)
		\item {Gr{\"u}ndete die Aachener Gruppe von FMB mit und leitete ein Team von Freiwilligen, das mindestens einmal pro Woche hausgemachte und gesunde Mahlzeiten f{\"u}r Studenten in und um Aachen bereitstellt.}
		\item {Organisierte Essensverteilungen zu festlichen Gelegenheiten, insbesondere im Ramadan.}
%		\item {Co-developed low-cost, sustainable standard operating model to make community effort scalable and reproducible at other locations.}
	\end{cvitems}%
}

\cvPositionFlush
%---------------------------------------------------------

\cvPositionOrganisation{EN}{Training and Placement Cell} % Organisation
\cvPositionOrganisation{DE}{Training and Placement Cell} % Organisation

\cvPositionPost{EN}{Assistant Head Coordinator, Dept of Electrical Engineering} % Post
\cvPositionPost{DE}{Assistant Head Coordinator, Dept of Electrical Engineering} % Post

\cvPositionLocation{EN}{\href{https://www.iitp.ac.in}{IIT Patna}, India \ifbool{showEmojis} {\space\emoji{flag-india}} {} } % Location
\cvPositionLocation{DE}{\href{https://www.iitp.ac.in}{IIT Patna}, Indien \ifbool{showEmojis} {\space\emoji{flag-india}} {} } % Location

\cvPositionDates{EN}{Apr. 2017 -- Apr. 2018} % Date(s)
\cvPositionDates{DE}{Apr. 2017 -- Apr. 2018} % Date(s)

\cvPositionDescription{EN}{%
	\begin{cvitems} % Description(s)
		\item {Selected by class majority to represent students of Dept of Electrical Engineering.}
%		\item {Led team in designing placement brochures and helped arrange on-campus placement sessions, tests and interviews.} % TODO @hatimak: German version not written yet
	\end{cvitems}%
}
\cvPositionDescription{DE}{%
	\begin{cvitems} % Description(s)
		\item {Von der Studentenschaft gew{\"a}hlt, um die Studenten des Fachbereichs Elektrotechnik zu repr{\"a}sentieren.}
	\end{cvitems}%
}

%\cvPositionFlush
%---------------------------------------------------------

\cvPositionOrganisation{EN}{Startup Relations, Entrepreneurship Club} % Organisation
\cvPositionOrganisation{DE}{Startup Relations, Entrepreneurship Club} % Organisation

\cvPositionPost{EN}{Coordinator} % Post
\cvPositionPost{DE}{Coordinator} % Post

\cvPositionLocation{EN}{\href{https://www.iitp.ac.in}{IIT Patna}, India \ifbool{showEmojis} {\space\emoji{flag-india}} {} } % Location
\cvPositionLocation{DE}{\href{https://www.iitp.ac.in}{IIT Patna}, Indien \ifbool{showEmojis} {\space\emoji{flag-india}} {} } % Location

\cvPositionDates{EN}{Apr. 2016 -- Apr. 2017} % Date(s)
\cvPositionDates{DE}{Apr. 2016 -- Apr. 2017} % Date(s)

\cvPositionDescription{EN}{%
	\begin{cvitems} % Description(s)
		\item {Served as department leader and offered mentorship to early-stage on-campus startups.}
		\item {Oversaw the organisation of annual national-level event E-Week 2017.}
		\item {Delivered lectures as part of In-house Mentorship series.} % TODO @hatimak: German version not written yet
	\end{cvitems}%
}
\cvPositionDescription{DE}{%
	\begin{cvitems} % Description(s)
		\item {Leitete die Abteilung und bot Mentorenschaft f{\"u}r Start-ups auf dem Campus an.}
		\item {Leitete die Organisation der j{\"a}hrlichen nationalen Veranstaltung E-Week 2017.}
	\end{cvitems}%
}

\cvPositionFlush
%---------------------------------------------------------

\cvPositionOrganisation{EN}{Startup Relations, Entrepreneurship Club} % Organisation
\cvPositionOrganisation{DE}{Startup Relations, Entrepreneurship Club} % Organisation

\cvPositionPost{EN}{Task Manager} % Post
\cvPositionPost{DE}{Task Manager} % Post

\cvPositionLocation{EN}{\href{https://www.iitp.ac.in}{IIT Patna}, India \ifbool{showEmojis} {\space\emoji{flag-india}} {} } % Location
\cvPositionLocation{DE}{\href{https://www.iitp.ac.in}{IIT Patna}, Indien \ifbool{showEmojis} {\space\emoji{flag-india}} {} } % Location

\cvPositionDates{EN}{Apr. 2015 -- Apr. 2016} % Date(s)
\cvPositionDates{DE}{Apr. 2015 -- Apr. 2016} % Date(s)

\cvPositionDescription{EN}{%
	\begin{cvitems} % Description(s)
		\item {Coordinated organisation of pitching events, workshops and guest talks.}
%		\item {Helped establish a panel of early investors and mentors for on-campus startups.} % TODO @hatimak: German version not written yet
	\end{cvitems}%
}
\cvPositionDescription{DE}{%
	\begin{cvitems} % Description(s)
		\item {Koordinierte die Organisation von Pitching-Veranstaltungen, Workshops und Gastvorstellungen.}
	\end{cvitems}%
}

%\cvPositionFlush
%---------------------------------------------------------

\end{cvpositions}
