\begin{cvProjects}

\cvProjectTitle{EN}{Software Developer} % Title
\cvProjectTitle{DE}{} % Title

\cvProjectOrganisation{EN}{\href{https://github.com/librecores/gsoc-museum-edsac}{``EDSAC Museum on FPGA''}\newline \href{https://fossi-foundation.org}{Free and Open Source Silicon Foundation}} % Organization
\cvProjectOrganisation{DE}{} % Organization

\cvProjectLocation{EN}{\href{https://summerofcode.withgoogle.com/archive/2017/projects/6470218444439552/}{Google Summer of Code 2017} \ifbool{showEmojis} {\space\emoji{globe-showing-asia-australia}} {} } % Location
\cvProjectLocation{DE}{} % Location

\cvProjectDates{EN}{May 2017 -- Aug. 2017} % Date(s)
\cvProjectDates{DE}{} % Date(s)

\cvProjectDescription{EN}{%
	\begin{cvitems} % Description(s)
		\item {Built Verilog model of historic EDSAC computer from original but incomplete documentation in collaboration with experts from The National Museum of Computing, UK.}
		\item {Programmed and simulated EDSAC architecture and ISA on \href{https://mystorm.uk/}{myStorm} Lattice iCE FPGA board using open-source toolchains, like \href{http://www.clifford.at/yosys/}{\texttt{Yosys}} and \href{http://iverilog.icarus.com}{\texttt{iverilog}}.}
		\item {Designed and implemented modified-UART communication protocol to support external embedded I/O interfaces for Hardware-in-Loop application.}
		% \item {Coordinated with team of students in UK to build hardware imitation of EDSAC memory delay line, teleprinter and paper tape reader.}
		\item {Demonstrated final work product at \href{http://chiphack.org/chiphack-2017.html}{ChipHack 2017 workshop} and \href{https://youtu.be/EZkJOyOcYiY}{presented} at \href{https://orconf.org/2017/\#edsac}{ORConf 2017 digital design conference} in Hebden Bridge, UK. Received full sponsorship.}
	\end{cvitems}%
}
\cvProjectDescription{DE}{}

% Uncomment following line to include this Project subsection in final document
\cvProjectFlush
%---------------------------------------------------------

\cvProjectTitle{EN}{Software Developer} % Title
\cvProjectTitle{DE}{} % Title

\cvProjectOrganisation{EN}{\href{https://www.coreboot.org}{Coreboot} (\href{https://www.flashrom.org/Flashrom}{Flashrom}), \href{https://drive.google.com/drive/u/1/folders/0B-Cccp-WWmeuUlh5M3pxT0cyQm8}{``Read/Write Multiple Status Registers and Lock/Unlock Memory on SPI Chips''}} % Organization
\cvProjectOrganisation{DE}{} % Organization

\cvProjectLocation{EN}{\href{https://summerofcode.withgoogle.com/archive/2016/projects/5439533130711040/}{Google Summer of Code 2016} \ifbool{showEmojis} {\space\emoji{globe-showing-asia-australia}} {} } % Location
\cvProjectLocation{DE}{} % Location

\cvProjectDates{EN}{Apr. 2016 -- Aug. 2016} % Date(s)
\cvProjectDates{DE}{} % Date(s)

\cvProjectDescription{EN}{%
	\begin{cvitems} % Description(s)
		\item {Designed unified model for abstraction of status registers, configuration bits, and memory protected areas in SPI Flash-memory chips across diverse chip manufacturers.}
		% \item {Programmed routines to lock/unlock memory areas, handle configuration bits, and automatically generate memory protection maps.}
		\item {Developed CLI to expose new features, and tested infrastructure using Raspberry Pi and microcontroller development board.}
		\item {Liaised with SPI chip manufacturers from China to arrange for engineering samples and add support for those chips.}
	\end{cvitems}%
}
\cvProjectDescription{DE}{}

% Uncomment following line to include this Project subsection in final document
\cvProjectFlush
%---------------------------------------------------------

% Title
\cvProjectTitle{EN}{Implementation of Normalised LMS Adaptive Filtering Algorithm for Signal Enhancement}
\cvProjectTitle{DE}{}

% Subtitle
\cvProjectOrganisation{EN}{Supervisor: Dr Yatendra Kumar Singh}
\cvProjectOrganisation{DE}{}

% Location
\cvProjectLocation{EN}{Design Lab, IIT Patna, India \ifbool{showEmojis} {\space\emoji{flag-india}} {} }
\cvProjectLocation{DE}{}

% Date(s)
\cvProjectDates{EN}{Oct. 2016 -- Dec. 2016}
\cvProjectDates{DE}{}

% Description(s)
\cvProjectDescription{EN}{%
	\begin{cvitems}
		\item {Implemented normalised LMS adaptive filtering to extract desired signal from that corrupted with autoregressive noise.}
		\item {Prototyped on Raspberry Pi Model 3.}
	\end{cvitems}%
}
\cvProjectDescription{DE}{}

% Uncomment following line to include this Experience subsection in final document
%\cvProjectFlush
%---------------------------------------------------------

% Title
\cvProjectTitle{EN}{Full-Custom Design of Ring Oscillator}
\cvProjectTitle{DE}{}

% Subtitle
\cvProjectOrganisation{EN}{Supervisor: Dr Kailash Chandra Ray}
\cvProjectOrganisation{DE}{}

% Location
\cvProjectLocation{EN}{VLSI Design Lab, IIT Patna, India \ifbool{showEmojis} {\space\emoji{flag-india}} {} }
\cvProjectLocation{DE}{}

% Date(s)
\cvProjectDates{EN}{Oct. 2016 -- Dec. 2016}
\cvProjectDates{DE}{}

% Description(s)
\cvProjectDescription{EN}{%
	\begin{cvitems}
		\item {Designed core layout of ring oscillator using AMI05 (0.5 um) CMOS Technology in Pyxis Layout (Mentor Graphics).}
	\end{cvitems}%
}
\cvProjectDescription{DE}{}

% Uncomment following line to include this Experience subsection in final document
%\cvProjectFlush
%---------------------------------------------------------

% Title
\cvProjectTitle{EN}{Biometric Attendance System for Economic and Low-power Limited-connectivity Remote Deployment}
\cvProjectTitle{DE}{Biometric Attendance System for Economic and Low-power Limited-connectivity Remote Deployment}

% Subtitle
\cvProjectOrganisation{EN}{Innovation Centre}
\cvProjectOrganisation{DE}{Innovation Centre}

% Location
\cvProjectLocation{EN}{\href{https://www.iitp.ac.in}{IIT Patna}, India \ifbool{showEmojis} {\space\emoji{flag-india}} {} }
\cvProjectLocation{DE}{\href{https://www.iitp.ac.in}{IIT Patna}, Indien \ifbool{showEmojis} {\space\emoji{flag-india}} {} }

% Date(s)
\cvProjectDates{EN}{Jan. 2015 -- Oct. 2015}
\cvProjectDates{DE}{Jan. 2015 -- Okt. 2015}

% Description(s)
\cvProjectDescription{EN}{%
	\begin{cvitems}
		\item {Led a team of 5 engineers and managed project deliverables.} % TODO: Add DE
		\item {Interfaced Atmel AT89S51 8051 microcontroller with R305 fingerprint reader and SIM900A GSM/GPRS module over serial port via multiplexer.}
		\item {Developed user interface using $16 \times 2$ LCD and keypad.}
		\item {Developed firmware in C and ASM. Microcontroller operations simulated in Proteus.}
	\end{cvitems}%
}
\cvProjectDescription{DE}{%
	\begin{cvitems}
		\item {Interfaced Atmel AT89S51 8051 microcontroller with R305 fingerprint reader and SIM900A GSM/GPRS module over serial port via multiplexer.}
		\item {Developed user interface using $16 \times 2$ LCD and keypad.}
		\item {Developed firmware in C and ASM. Microcontroller operations simulated in Proteus.}
	\end{cvitems}%
}

% Uncomment following line to include this Experience subsection in final document
%\cvProjectFlush
%---------------------------------------------------------

\end{cvProjects}